\sysfull

### 2017-08-11 paper/coalescing.tex

\noindent\textbf{Task Coalescing Implementation:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes tasks in the first operating period, assigning the \emph{half of sum of all previous $S$ periods} (in the example case: $C=8/2$). \sys completes then coalesced tasks successfully (four tasks were executed) and in the next operating period, i.e. $C=(8+4)/2$. In the third task execution, power fails after the second task. Then \sys re-executes coalesced task since the previous failure and sets $C=(6+8+2)/2$ in the next operating period. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

>>>>

\noindent\textbf{Task Coalescing Illustration:} Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes tasks in the first operating period, assigning the \emph{half of sum of all previous $S$ periods} (in the example case: $C=8/2$). \sys completes then coalesced tasks successfully (four tasks were executed) and in the next operating period, i.e. $C=(8+4)/2$. In the third task execution, power fails after the second task. Then \sys re-executes coalesced task since the previous failure and sets $C=(6+8+2)/2$ in the next operating period. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

### 2017-08-11 paper/intro.tex

In this work we develop {\bf \sys}: a new programming and execution model efficiently executing tasks which avoids non-termination across a range of energy buffer sizes, without burdening the programmer. To accomplish this, \sys introduces new capabilities:

>>>>

In this work we develop {\bf \sys}: a new programming and execution model efficiently executing tasks which avoids non-termination across a range of energy buffer sizes, without burdening the programmer\footnote{Code will be available via \href{http://anonymized.link}{http://anonymized.link}.}. To accomplish this, \sys introduces new capabilities:

### 2017-08-11 paper/systemdescription.tex

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{task foo(){...}} & Task declaration\\
		\texttt{origin task foo(){...}} & Origin task declaration\\
		\texttt{next\_task()} & Transition to a new task\\
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\hline
	\end{tabular}
	\caption{Summary of \sys's programming model extensions.\todo{Revise this table (confusion with next\_task() function)}{Amjad/Przemek}}
	\label{tab:viper_syntax}
\end{table}

\noindent \textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through a {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and a {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM\todo{Sentence unclear}{Brandon}. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{task foo(){...}} & Task declaration\\
		\texttt{origin task foo(){...}} & Origin task declaration\\
		\texttt{next\_task()} & Transition to a new task\\
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\hline
	\end{tabular}
	\caption{Summary of \sys's programming model extensions.}
	\label{tab:viper_syntax}
\end{table}

\noindent \textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through a {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and a {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.
